Multi sky-view\\ 3D aerosol distribution recovery

### 2013-09-30 article.tex
Replaced pdf_tex images with pdf (to avoid text placement problems). Using textext extension in inkscape based on http://people.orie.cornell.edu/jmd388/design/
bookmark

\usepackage{opex3}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}
\usepackage[]{todonotes} % Add option [disable] to hide all todo notes.
\usepackage{xfrac}
\usepackage{paralist}
\usepackage{cite}
\usepackage{soul}

@@

\begin{document}

@@

The MC simulations rely on the same grid as
\cref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per pixel (\cref{fig:mcgrid}(a)):
\begin{figure}
  \centering
  \yoavcomment{\def\svgwidth{\linewidth}\small{\input{images/mcgrid.pdf_tex}}}
  \caption{\small [a] Multiple-scattering forward model by MC.
    [b] Photograph of the same sky and view point as in
    \cref{fig:simulation-results1}[left], rendered using MC.
    [c] Cross section along the $X$-Axis of the MC simulation,
    single-scattering simulation and a single-scattering image created
    from the reconstructed distribution
    (\cref{sec:optimization-results}).}
  \label{fig:mcgrid}
\end{figure}

@@

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}[left].  A
comparison of a sample horizontal cross section is shown in
\cref{fig:mcgrid}(c).

@@

\begin{figure}[h]
  \centering
  \yoavcomment{\def\svgwidth{0.6\linewidth}\small{\input{images/error_vs_cameras.pdf_tex}}}
  \caption{\small Local error measure as function of cameras
    quantity. The blue error bars represent the error standard
    deviation. The dashed horizontal line marks the reconstruction
    error when all thirty six cameras are used.}
  \label{fig:error_vs_cameras}
\end{figure}

>>>>

\usepackage{opex3}
\usepackage{times}
\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{bm}
\usepackage{enumerate}
\usepackage[]{todonotes} % Add option [disable] to hide all todo notes.
\usepackage{xfrac}
\usepackage{paralist}
\usepackage{cite}
\usepackage{soul}
\usepackage{layouts}

@@

\begin{document}
%\printinunitsof{in}\prntlen{\linewidth}

@@

The MC simulations rely on the same grid as
\cref{sec:single-scatt-model}. We use backward MC: from a detector
pixel, photons are `launched' via the camera lens; then the photons
are traced back through the atmosphere. Photons that happen to be
back-traced to the Sun are counted, per pixel. In this model, RT takes
the following steps, per pixel (\cref{fig:mcgrid}(a)):
\begin{figure}
  \centering
  \yoavcomment{\includegraphics{images/mcgrid.pdf}}
  \caption{\small [a] Multiple-scattering forward model by MC.
    [b] Photograph of the same sky and view point as in
    \cref{fig:simulation-results1}[left], rendered using MC.}
  \label{fig:mcgrid}
\end{figure}

@@

The quality of MC increases with the number of photons launched.
\Cref{fig:mcgrid}(b) shows a photograph of the {\em Haze Blobs}
scene, derived by the MC process, using \num{10000} photons per pixel,
from the same viewpoint as \cref{fig:simulation-results1}[left].
Comparison of \hl{horizontal and vertical cross sections along 
matching MC and single-scattering simulated images are} shown in
\cref{fig:cross_sections}(a) and \cref{fig:cross_sections}(b).
\hl{The cross sections indicate fair correspondence between
the MC and single-scattering simulations.}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/cross_sections.pdf}}
  \caption{\small Cross sections along the $X$-Axis [a] and $Y$-Axis [b] of
    a MC and single-scattering simulations. Overlay of the cross
    sections on the MC simulated image is shown in [c]. }
  \label{fig:cross_sections}
\end{figure}

\Cref{fig:scatter_order} \hl{shows the contribution of subsequent
scattering events to the MC image. The amount of light scattered
in the direction of the sun due to the first scatter event of each photon
is collected to create} \cref{fig:scatter_order}(a). \hl{This process
is repeated for the second and third scatter events creating}
\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c),
\hl{respectively. It is conspicuous that the first scatter is responsible
for most of the energy in the MC image. The effect of subsequent scatters
is mostly evident at the horizon. The line of sight extending into the
horizon crosses a larger volume of atmosphere then the line of sight extending
in the direction of the zenith. This increases the probability of
scattering events along the line of sight extending into the horizon.}
\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order2.pdf}}
  \caption{\small Separation of a MC simulated image to (a) first
   scattering order, (b) second scattering order and (c) third
   scattering order. }
  \label{fig:scatter_order}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \yoavcomment{\includegraphics{images/error_vs_cameras.pdf}}
  \caption{\small Local error measure as function of cameras
    quantity. The blue error bars represent the error standard
    deviation. The dashed horizontal line marks the reconstruction
    error when all thirty six cameras are used.}
  \label{fig:error_vs_cameras}
\end{figure}
